\bf\mftitle

### 2011-03-01 doc/jInfer/projecttype/projecttype.tex
Documentation: ProjectType module: review round 1 part 4.

\begin{figure}
	\subfigure[Legend: Rectangle is folder, Rounded rectangle is file] {
		\centering\includegraphics[scale=\myscale]{project_dir_structure}
	}
	\caption{Project directory structure} \label{dir-structure}
\end{figure}

For each jInfer project a specific directory structure in the filesystem describing this project is created. This structure is described in figure \ref{dir-structure}. A folder in the filesystem is considered to be jInfer project folder iff it contains a \emph{jinferproject} subfolder. This folder contains two files: \emph{project.properties}, where all properties set for that particular project are stored. The second file is \emph{input.files} which is an XML file filled with paths to files selected particular project input (structure of this file is described in section \ref{input.files}). \emph{output} subfolder contains schema files which were generated by jInfer inference runs.

@@

Structure of \jmodule{ProjectType} can be divided into the following five main parts.
\begin{itemize}
	\item Base classes - classes providing core functionality like project creation and definitions of operations like move, delete, copy etc. All the base classes are contained in the \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype} package.
	\item Visualization classes - these classes create tree structure of jInfer project in NBP Projects view and are contained in the \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.nodes}.
	\item Actions - classes from \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.actions} package that provide actions allowing adding input files into the project, removing input files, or running the inference on the project.
	\item Properties - classes responsible for creation of project properties window with properties category tree. These are located in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.properties} package.
	\item Project wizard - classes representing new project creation through a project wizard from \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.sample} package.
\end{itemize}

@@

\begin{figure}
	\centering\includegraphics[scale=\myscale]{node_structure}
	\caption{Project nodes structure} \label{node-structure}
\end{figure}

@@

A category in the properties window is represented by NBP \code{ProjectCustomizer.Category} class, properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From jInfer module point of view the properties category is represented by \code{PropertiesPanelProvider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project properties window is described in section \ref{properties_reg}.\\

\code{JInferComponentProvider} is a very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizerProvider} class (which extends NBP \code{CustomizerProvider} class) is the core functionality of collecting categories (\code{PropertiesPanelProvider} interface) with associated properties panes (\code{AbstractPropertiesPanel} class) from all jInfer modules.\\

@@

\noindent\code{PropertiesPanelProvider} interface provides the following methods:
\begin{itemize}
	\item getName() - gets a programmatic name of this category.
	\item getDisplayName() - gets a name of this category which will be displayed in properties window.
	\item getPriority() - gets priority of this category, by which it is sorted among other sibling categories in the tree.
	\item getPanel(Properties) - gets the \code{AbstractPropertiesPanel} instance representing the category \emph{properties pane}. The only parameter is an instance of \code{Properties} class holding stored properties for the \emph{properties pane}.
	\item getParent() - getter for a programmatic name of category which is the parent of this category in the tree hierarchy.
	\item getSubCategories() - gets a \code{List} of \code{VirtualCategoryPanel} instances representing virtual category children.
\end{itemize}

@@

\begin{verbatim}
@ServiceProvider(service = PropertiesPanelProvider.class)
public class PropertiesPanelProviderImpl implements PropertiesPanelProvider{

  @Override
  public AbstractPropertiesPanel getPanel(final Properties properties) {
    return new ExamplePropertiesPanel(properties);
  }

@@

  @Override
  public List<VirtualCategoryPanel> getSubCategories() {
    final List<VirtualCategoryPanel> result = new ArrayList<VirtualCategoryPanel>();
    result.add(new VirtualCategoryPanel("virtual_categoryID", "example virtual category",
            ModuleSelectionHelper.lookupImpls(IGGenerator.class)));

@@

\noindent\code{VirtualCategoryPanel} extends \code{JPanel}, its constructor has three parameters:
 \begin{itemize}
	\item \code{categoryId} - programmatic name of the category or ID.
	\item \code{categoryName} - human readable name of the category displayed in jInfer properties window.
	\item \code{modules} - \code{List<?\ extends NamedModule>} of modules that will be children of this virtual category.
\end{itemize}

@@

  public ExamplePropertiesPanel(final Properties properties) {
    super(properties);
    init();
  }

@@

\noindent \code{RunningProject} class implements these methods:
\begin{itemize}
	\item \code{setActiveProject()} - setter of the \code{JInferProject} instance of a running project, which sets the \code{JInferProject} instance if no other inference is running (no other \code{JInferProject} instance is already set). Returns \code{boolean} value, based on whether the setting was successful.
	\item \code{removeActiveProject()} - removes the \code{JInferProject} instance if some inference is running.
	\item \code{getActiveProject()} - getter of the \code{JInferProject} instance of a running project.
	\item \code{isActiveProject()} - checks if some inference is running (the \code{JInferProject} instance is set).
	\item \code{getActiveProjectProps()} - gets the \code{Properties} instance from the actual running inference (\code{Properties} instance is part of the \code{JInferProject} instace). If no project is running at the moment, an empty \code{Properties} instance is returned - this allows the JUnit tests to run with default settings.
	\item \code{getNextModuleCaps()} - getter of capabilities of the next module in the inference chain.
	\item \code{setNextModuleCaps()} - setter of capabilities of the next module in the inference chain.
\end{itemize}

>>>>

\begin{figure}
	\subfigure[Legend: Rectangle is folder, Rounded rectangle is file.] {
		\centering\includegraphics[scale=\myscale]{project_dir_structure}
	}
	\caption{Project directory structure.} \label{dir-structure}
\end{figure}

For each jInfer project a specific directory structure in the filesystem describing this project is created. This structure is described in figure \ref{dir-structure}. A folder in the filesystem is considered to be jInfer project folder if it contains a \emph{jinferproject} subfolder. This folder contains two files: \emph{project.properties}, where all properties set for that particular project are stored. The second file is \emph{input.files} which is an XML file filled with paths to files selected as particular project input (structure of this file is described in section \ref{input.files}). \emph{output} subfolder contains schema files which were generated by jInfer inference runs.

@@

Structure of \jmodule{ProjectType} can be divided into the following five main parts.
\begin{itemize}
	\item Base classes - Classes providing core functionality like project creation and definitions of operations like move, delete, copy etc. All the base classes are contained in the \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype} package.
	\item Visualization classes - These classes create tree structure of jInfer project in NBP Projects view and are contained in the \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.nodes}.
	\item Actions - Classes from \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.actions} package that provide actions allowing adding input files into the project, removing input files, or running the inference on the project.
	\item Properties - Classes responsible for creation of project properties window with properties category tree. These are located in \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.properties} package.
	\item Project wizard - Classes representing new project creation through a project wizard from \code{cz.\.cuni.\.mff.\.ksi.\.jinfer.\.projecttype.\.sample} package.
\end{itemize}

@@

\begin{figure}
	\centering\includegraphics[scale=\myscale]{node_structure}
	\caption{Project nodes structure.} \label{node-structure}
\end{figure}

@@

A category in the properties window is represented by NBP \code{ProjectCustomizer.Category} class, properties pane is represented by \code{JPanel} class. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}. From jInfer module point of view the properties category is represented by \code{Properties\-Panel\-Provider} interface and associated properties pane by \code{AbstractPropertiesPanel} abstract class. How to use this interface and abstract class to create custom project properties category presented in jInfer project properties window is described in section \ref{properties_reg}.\\

\code{JInferComponentProvider} is a very simple class that extends \code{ProjectCustomizer.CategoryComponentProvider} class from NBP and its only method is \code{create()} which takes category as a parameter and returns properties pane. In the \code{JInferCustomizer\-Provider} class (which extends NBP \code{CustomizerProvider} class) is the core functionality of collecting categories (\code{PropertiesPanelProvider} interface) with associated properties panes (\code{AbstractPropertiesPanel} class) from all jInfer modules.\\

@@

\noindent\code{PropertiesPanelProvider} interface provides the following methods:
\begin{itemize}
	\item getName() - Gets a programmatic name of this category.
	\item getDisplayName() - Gets a name of this category which will be displayed in properties window.
	\item getPriority() - Gets priority of this category, by which it is sorted among other sibling categories in the tree.
	\item getPanel(Properties) - Gets the \code{AbstractPropertiesPanel} instance representing the category \emph{properties pane}. The only parameter is an instance of \code{Properties} class holding stored properties for the \emph{properties pane}.
	\item getParent() - Getter for a programmatic name of category which is the parent of this category in the tree hierarchy.
	\item getSubCategories() - Gets a \code{List} of \code{VirtualCategoryPanel} instances representing virtual category children.
\end{itemize}

@@

\begin{verbatim}
@ServiceProvider(service = PropertiesPanelProvider.class)
public class PropertiesPanelProviderImpl implements PropertiesPanelProvider {

  @Override
  public AbstractPropertiesPanel getPanel(Properties properties) {
    return new ExamplePropertiesPanel(properties);
  }

@@

  @Override
  public List<VirtualCategoryPanel> getSubCategories() {
    List<VirtualCategoryPanel> result = new ArrayList<VirtualCategoryPanel>();
    result.add(new VirtualCategoryPanel("virtual_categoryID", "example virtual category",
            ModuleSelectionHelper.lookupImpls(IGGenerator.class)));

@@

\noindent\code{VirtualCategoryPanel} extends \code{JPanel}, its constructor has three parameters:
 \begin{itemize}
	\item \code{categoryId} - Programmatic name of the category or ID.
	\item \code{categoryName} - Human readable name of the category displayed in jInfer properties window.
	\item \code{modules} - \code{List<?\ extends NamedModule>} of modules that will be children of this virtual category.
\end{itemize}

@@

  public ExamplePropertiesPanel(Properties properties) {
    super(properties);
    init();
  }

@@

\noindent \code{RunningProject} class implements these methods:
\begin{itemize}
	\item \code{setActiveProject()} - Setter of the \code{JInferProject} instance of a running project, which sets the \code{JInferProject} instance if no other inference is running (no other \code{JInferProject} instance is already set). Returns \code{boolean} value, based on whether the setting was successful.
	\item \code{removeActiveProject()} - Removes the \code{JInferProject} instance if some inference is running.
	\item \code{getActiveProject()} - Getter of the \code{JInferProject} instance of a running project.
	\item \code{isActiveProject()} - Checks if some inference is running (the \code{JInferProject} instance is set).
	\item \code{getActiveProjectProps()} - Gets the \code{Properties} instance from the actual running inference (\code{Properties} instance is part of the \code{JInferProject} instace). If no project is running at the moment, an empty \code{Properties} instance is returned - this allows the JUnit tests to run with default settings.
	\item \code{getNextModuleCaps()} - Getter of capabilities of the next module in the inference chain.
	\item \code{setNextModuleCaps()} - Getter of capabilities of the next module in the inference chain.
\end{itemize}
